Manuscript

### 2023-05-26 Manuscript1.Rmd
updates

```{r}
#plot parameterrecovery
plot_parameterrecovery(rw_pp, div = F, subs = 5)

plot_parameterrecovery(wb_pp, div = F, subs = 5)

plot_parameterrecovery(kalman_pp, div = T, subs = 5)

@@

mu_b1 = 2
sd_b1 = 0.5

mu_b2 = 0.1
sd_b2 = 0.5

>>>>

files = paste0(here::here("workspace","parameterrecovery"),"/",list.files(here::here("workspace","parameterrecovery")))

#plot parameterrecovery
load(files[[2]])
q = lapply(here("scripts", scripts), source)
rwplot = plot_parameterrecovery(rw_pp, div = T, subs = 5)
load(files[[3]])
q = lapply(here("scripts", scripts), source)
wbplot = plot_parameterrecovery(wb_pp, div = T, subs = 5)
load(files[[1]])
q = lapply(here("scripts", scripts), source)
kalmanplot = plot_parameterrecovery(kalman_pp, div = T, subs = 5)

layout = (c(
  area(1, 1, 2,3),
  area(3, 1,5,3),
  area(6, 1,6,3)

plot(layout)

((rwplot[[1]]+wbplot[[1]]+kalmanplot[[1]])/(rwplot[[2]]+wbplot[[2]]+kalmanplot[[2]])/((rwplot[[3]]+wbplot[[3]]+kalmanplot[[3]])))+
  plot_annotation(tag_levels = 'A')+
  plot_layout(design = layout,guides = 'collect')

@@

mu_b1 = seq(0.1,2,length.out = 5)
sd_b1 = seq(0.1,2,length.out = 3)

mu_b2 = seq(0.1,2,length.out = 5)
sd_b2 = seq(0.1,2,length.out = 3)
